### 2009-11-19 doc/manuals/janitor/tex_maintenance/maintenance.tex
Some rewording, but otherwise a fine.

The Catalog describes runtime environments and is either served through a web server or is distributed together with the Janitor as a regular file. 
It is specifed by a (Resource Description Framework) RDF file assigned to 
Janitor using the tag \texttt{catalog} within the configuration file (see~\ref{sec:janitor_configuration}). 
The format of the RDF file is defined by a RDF schema file \texttt{knowarc.rdfs}
which can be found along with an RDF example file \texttt{knowarc.rdf} in the janitor source directory \href{http://svn.nordugrid.org/repos/nordugrid/arc1/trunk/src/services/janitor/resources/catalog/}
{http://svn.nordugrid.org/repos/nordugrid/arc1/trunk/src/services/janitor/resources/catalog/}.\\

In order to adminstrate the catalog, the ontology editor Prot\`eg\`e should be used. Figure~\ref{fig:protege_example} shows the
editor while the MetaPackage \texttt{APPS/BIO/JASPAR-CORE-1.0} of the example file has been selected.
\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{images/protege_JASPAR.png}
    \mycaption{Example of a RDF catalog file as displayed in the program Prot\`eg\`e.}{}
    \label{fig:protege_example}
  \end{center}
\end{figure}
On the left side of the editor the class browser is placed. Three main classes are prepared: \texttt{MetaPackage}, \texttt{Note} and \texttt{Package}.
The \texttt{Metapackage} is a general platform independent description of a \texttt{Package}. 
It has one or more instances of the class \texttt{Package} and is
described by the subclasses of \texttt{Note}. The class \texttt{Note} has two subclasses: \texttt{BaseSystem} 
and \texttt{Tag} to describe the \texttt{MetaPackage}. The \texttt{BaseSystem} describes the Debian release a \texttt{Package} refers to
(i.e. here etch or sid), i.e. the name of a common installation or a virtual image.
The class \texttt{Tag} provides small keywords which can be assigned to \texttt{MetaPackages} such that
they can be found more easily.  \texttt{TarPackage} and \texttt{DebianPackage} or currently the only subclasses of \texttt{Package}.
They are representing the necessary information (i.e. URL or Packagename) for the installation. In order to have an overview how the 
classes are interacting with each other the tables~\ref{tab:main_class_meta}, \ref{tab:main_class_base}, \ref{tab:main_class_tag},
\ref{tab:main_class_debian} and \ref{tab:main_class_tar} are pictured.

@@

This section describes how to add new packages to the Catalog. In the current implementation, only tar based packages are processed by the Janitor.
Within the example they are assigned to be used together with Debian Etch. This limitation is only literal. 
There is no limitiation to newer Debian distributions.

@@

At the time of writing, only the tape archive (tar) file format is accepted for dynamic Runtime Environment installation, 
a well accepted file format throughout the UNIX community. The reflects the traditional manual approach towards RTE in ARC,
for which one directory is made available to all compute nodes. This section explains the inner structure of the tar files. 
Subdirectories are visualised in Figure~\ref{fig:tar_folder}.

@@

From such Catalogues, the Janitor finds all information to install packages that possibly have never been installed
on the site before. The offers of RTEs in a catalogue are cross-checked against the local infrastructure and a subset
of the available packages will be accepted as "installable". This list of installable RTEs is forwarded to the
grid information system.

@@

The WEKA package for machine learning~\cite{FRANK_20074} and the Java Runtime Environment
are available as dynamic Runtime Environments. Further packages for bioinformatics comprise dynamic
variants of tools for the analysis of transcription factor binding sites. These are already offered for manual
installation via the prior mentioned traditional page representing Runtime Environments for ARC. 
The corresponding tar file is named \task{somewhat??}. The \texttt{data} directory simply contains a ZIP file
which needs to be unzipped in the installation directory. For that reason, the \texttt{control/install} script is 
written as follows:
% dollar signs made trouble in listings *hrmlgrmpf* ... Costs too much time to figure out why *ARC!*
\begin{verbatim} 
#!/bin/sh
set -e  # Makes the script to terminate at the first line it fails.

@@

WEKA_JAR="weka-3-4-8a/weka.jar"
case "\$1" in
	0)	# Just before job submission
		# none
	;;
	1)	# Just before job execution
		# Initialize the java environment
		CLASSPATH="%BASEDIR%/$WEKA_JAR:$CLASSPATH"
		export CLASSPATH
	;;
	2)	# After job termination
		# none
	;;
	*)
		return 1
	;;
esac	
\end{verbatim}
The remove script, which will be executed right before WEKA is deinstalled, is empty. Janitor will delete the directory, so there
is nothing more to be done.\\

@@

\section{Typical use cases}\label{sec:catalog}

>>>>

The Catalog describes runtime environments and is either served
through a web server or is distributed together with the Janitor as a
regular file.  It is specifed by a (Resource Description Framework)
RDF file assigned to Janitor using the tag \texttt{catalog} within
the configuration file (see~\ref{sec:janitor_configuration}).
The format of the RDF file is defined by an RDF schema file
\texttt{knowarc.rdfs} which can be found along with an RDF
example file \texttt{knowarc.rdf} in the Janitor source directory
\href{http://svn.nordugrid.org/repos/nordugrid/arc1/trunk/src/services/janitor/resources/catalog/}
{http://svn.nordugrid.org/repos/nordugrid/arc1/trunk/src/services/janitor/resources/catalog/}.

To edit the catalog, the ontology editor Prot\`eg\`e should be
used. Figure~\ref{fig:protege_example} shows the editor while the
MetaPackage \texttt{APPS/BIO/JASPAR-CORE-1.0} of the example file has
been selected.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{images/protege_JASPAR.png}
    \mycaption{Example of a RDF catalog file as displayed in the program Prot\`eg\`e.}{}
    \label{fig:protege_example}
  \end{center}
\end{figure}

On the left side of the editor the class browser is placed.  Three
main classes are prepared: \texttt{MetaPackage}, \texttt{Note}
and \texttt{Package}.  The \texttt{Metapackage} is a general
platform-independent description of a \texttt{Package}.  It has one
or more instances of the class \texttt{Package} and is described
by the subclasses of \texttt{Note}. The class \texttt{Note} has
two subclasses: \texttt{BaseSystem} and \texttt{Tag} to describe
the \texttt{MetaPackage}. The \texttt{BaseSystem} describes the
Debian release a \texttt{Package} refers to (i.e. here etch or
sid), i.e. the name of a common installation or a virtual image.
The class \texttt{Tag} provides small keywords which can be assigned
to \texttt{MetaPackages} such that they can be found more easily.
\texttt{TarPackage} and \texttt{DebianPackage} or currently the only
subclasses of \texttt{Package}.  They are representing the necessary
information (i.e. URL or Packagename) for the installation. In order
to have an overview how the classes are interacting with each other
the tables~\ref{tab:main_class_meta}, \ref{tab:main_class_base},
\ref{tab:main_class_tag}, \ref{tab:main_class_debian} and
\ref{tab:main_class_tar} are pictured.

@@

This section describes how to add new packages to the Catalog. In the
current implementation, only tar based packages are processed by the
Janitor.  Within the example they are assigned to be used together with
Debian Etch. This limitation is only literal.  There is no restriction
for newer Debian distributions.

@@

At the time of writing, only the tape archive (tar) file format is
accepted for dynamic Runtime Environment installation, a well accepted
file format throughout the UNIX community. The concept reflects the
traditional manual approach towards RTE in ARC, for which one directory
is made available to all compute nodes. This section explains the
inner structure of the tar files.  Subdirectories are visualised in
Figure~\ref{fig:tar_folder}.

@@

From such Catalogs, the Janitor finds all information to install
packages that possibly have never been installed on the site before. The
offers of RTEs in a Catalog are cross-checked against the local
infrastructure and a subset of the available packages will be accepted as
"installable". This list of installable RTEs is forwarded to the grid
information system.

@@

The WEKA package for machine learning~\cite{FRANK_20074} and the Java
Runtime Environment are available as dynamic Runtime Environments. Further
packages for bioinformatics comprise dynamic variants of tools for
the analysis of transcription factor binding sites. These are already
offered for manual installation via the prior mentioned traditional page
representing Runtime Environments for ARC.  The corresponding tar file
is named \task{somewhat??}. The \texttt{data} directory simply contains
a ZIP file which needs to be unzipped in the installation directory. For
that reason, the \texttt{control/install} script is written as follows:

% dollar signs made trouble in listings *hrmlgrmpf* ... Costs too much time to figure out why *ARC!*
\begin{verbatim} 
#!/bin/sh
set -e  # Makes the script to terminate at the first line it fails.

@@

WEKA_JAR="weka-3-4-8a/weka.jar"
case "\$1" in
	0)	# Just before job submission
		# none
	;;
	1)	# Just before job execution
		# Initialize the java environment
		CLASSPATH="%BASEDIR%/$WEKA_JAR:$CLASSPATH"
		export CLASSPATH
	;;
	2)	# After job termination
		# none
	;;
	*)
		return 1
	;;
esac	
\end{verbatim}

The remove script, which will be executed right before WEKA is deinstalled, is empty.
Janitor will delete the directory, so there is nothing more to be done.

@@

%\section{Typical use cases}\label{sec:catalog}
